Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-10-09 paper.tex
As submitted 100924
JCP requested no TOC image in and library built into body of text

\section{References}
% Create the reference section using BibTeX:
\bibliography{library.bib}

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{toc.png}
	\caption{
		TOC Image.
	} 
	\label{fig:toc}
\end{figure*}

>>>>

\section{References}
% Create the reference section using BibTeX:
%\bibliography{library.bib}
%apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
%Control: key (0)
%Control: author (72) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (-1) disabled
%Control: page (0) single
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{112}%
	\makeatletter
	\providecommand \@ifxundefined [1]{%
		\@ifx{#1\undefined}
	}%
	\providecommand \@ifnum [1]{%
		\ifnum #1\expandafter \@firstoftwo
		\else \expandafter \@secondoftwo
		\fi
	}%
	\providecommand \@ifx [1]{%
		\ifx #1\expandafter \@firstoftwo
		\else \expandafter \@secondoftwo
		\fi
	}%
	\providecommand \natexlab [1]{#1}%
	\providecommand \enquote  [1]{``#1''}%
	\providecommand \bibnamefont  [1]{#1}%
	\providecommand \bibfnamefont [1]{#1}%
	\providecommand \citenamefont [1]{#1}%
	\providecommand \href@noop [0]{\@secondoftwo}%
	\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
	\providecommand \@href[1]{\@@startlink{#1}\@@href}%
	\providecommand \@@href[1]{\endgroup#1\@@endlink}%
	\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
		`\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
	\providecommand \@@startlink[1]{}%
	\providecommand \@@endlink[0]{}%
	\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
	\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
	\providecommand \urlprefix  [0]{URL }%
	\providecommand \Eprint [0]{\href }%
	\providecommand \doibase [0]{https://doi.org/}%
	\providecommand \selectlanguage [0]{\@gobble}%
	\providecommand \bibinfo  [0]{\@secondoftwo}%
	\providecommand \bibfield  [0]{\@secondoftwo}%
	\providecommand \translation [1]{[#1]}%
	\providecommand \BibitemOpen [0]{}%
	\providecommand \bibitemStop [0]{}%
	\providecommand \bibitemNoStop [0]{.\EOS\space}%
	\providecommand \EOS [0]{\spacefactor3000\relax}%
	\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
	\let\auto@bib@innerbib\@empty
	%</preamble>
	\bibitem [{\citenamefont {Cho}(2008)}]{Cho2008}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
			{Cho}},\ }\href {https://doi.org/10.1021/cr078377b} {\bibfield  {journal}
		{\bibinfo  {journal} {Chemical Reviews}\ }\textbf {\bibinfo {volume} {108}},\
		\bibinfo {pages} {1331} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Oudar}\ and\ \citenamefont {Shen}(1980)}]{RN307}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~L.}\ \bibnamefont
			{Oudar}}\ and\ \bibinfo {author} {\bibfnamefont {Y.~R.}\ \bibnamefont
			{Shen}},\ }\href {https://doi.org/10.1103/PhysRevA.22.1141} {\bibfield
		{journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
			{22}},\ \bibinfo {pages} {1141} (\bibinfo {year} {1980})}\BibitemShut
	{NoStop}%
	\bibitem [{\citenamefont {Nguyen}\ and\ \citenamefont {Wright}(1985)}]{RN281}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~C.}\ \bibnamefont
			{Nguyen}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
			{Wright}},\ }\href
	{https://doi.org/https://doi.org/10.1016/0009-2614(85)80208-6} {\bibfield
		{journal} {\bibinfo  {journal} {Chemical Physics Letters}\ }\textbf {\bibinfo
			{volume} {117}},\ \bibinfo {pages} {224} (\bibinfo {year}
		{1985})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Wright}\ \emph {et~al.}(1991)\citenamefont {Wright},
		\citenamefont {Carlson}, \citenamefont {Hurst}, \citenamefont {Steehler},
		\citenamefont {Riebe}, \citenamefont {Price}, \citenamefont {Nguyen},\ and\
		\citenamefont {Lee}}]{RN103}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
			{Wright}}, \bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont {Carlson}},
		\bibinfo {author} {\bibfnamefont {G.~B.}\ \bibnamefont {Hurst}}, \bibinfo
		{author} {\bibfnamefont {J.~K.}\ \bibnamefont {Steehler}}, \bibinfo {author}
		{\bibfnamefont {M.~T.}\ \bibnamefont {Riebe}}, \bibinfo {author}
		{\bibfnamefont {B.~B.}\ \bibnamefont {Price}}, \bibinfo {author}
		{\bibfnamefont {D.~C.}\ \bibnamefont {Nguyen}},\ and\ \bibinfo {author}
		{\bibfnamefont {S.~H.}\ \bibnamefont {Lee}},\ }\href
	{https://doi.org/10.1080/01442359109353262} {\bibfield  {journal} {\bibinfo
			{journal} {International Reviews in Physical Chemistry}\ }\textbf {\bibinfo
			{volume} {10}},\ \bibinfo {pages} {349} (\bibinfo {year} {1991})}\BibitemShut
	{NoStop}%
	\bibitem [{\citenamefont {Gaynor}\ and\ \citenamefont
		{Khalil}(2017)}]{Gaynor2017}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
			{Gaynor}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
			{Khalil}},\ }\href {https://doi.org/10.1063/1.4991745} {\bibfield  {journal}
		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
			{volume} {147}},\ \bibinfo {pages} {094202} (\bibinfo {year}
		{2017})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Mandal}\ \emph {et~al.}(2018)\citenamefont {Mandal},
		\citenamefont {Ng~Pack}, \citenamefont {Shah}, \citenamefont {Erramilli},\
		and\ \citenamefont {Ziegler}}]{Ziegler2018}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
			{Mandal}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Ng~Pack}},
		\bibinfo {author} {\bibfnamefont {P.~P.}\ \bibnamefont {Shah}}, \bibinfo
		{author} {\bibfnamefont {S.}~\bibnamefont {Erramilli}},\ and\ \bibinfo
		{author} {\bibfnamefont {L.~D.}\ \bibnamefont {Ziegler}},\ }\href
	{https://doi.org/10.1103/PhysRevLett.120.103401} {\bibfield  {journal}
		{\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {120}},\
		\bibinfo {pages} {103401} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Song}\ \emph {et~al.}(2019)\citenamefont {Song},
		\citenamefont {Schubert}, \citenamefont {Maret}, \citenamefont {Burdick},
		\citenamefont {Dunietz}, \citenamefont {Geva},\ and\ \citenamefont
		{Ogilvie}}]{Ogilvie2019}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
			{Song}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Schubert}},
		\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Maret}}, \bibinfo
		{author} {\bibfnamefont {R.~K.}\ \bibnamefont {Burdick}}, \bibinfo {author}
		{\bibfnamefont {B.~D.}\ \bibnamefont {Dunietz}}, \bibinfo {author}
		{\bibfnamefont {E.}~\bibnamefont {Geva}},\ and\ \bibinfo {author}
		{\bibfnamefont {J.~P.}\ \bibnamefont {Ogilvie}},\ }\href
	{https://doi.org/10.1039/C9SC02329A} {\bibfield  {journal} {\bibinfo
			{journal} {Chem. Sci.}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages}
		{8143} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Vietze}\ \emph {et~al.}(2021)\citenamefont {Vietze},
		\citenamefont {Backus}, \citenamefont {Bonn},\ and\ \citenamefont
		{Grechko}}]{Bonn2021}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
			{Vietze}}, \bibinfo {author} {\bibfnamefont {E.~H.~G.}\ \bibnamefont
			{Backus}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bonn}},\ and\
		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Grechko}},\ }\href
	{https://doi.org/10.1063/5.0047918} {\bibfield  {journal} {\bibinfo
			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {154}},\
		\bibinfo {pages} {174201} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Daniels}\ \emph {et~al.}(2022)\citenamefont
		{Daniels}, \citenamefont {Wells},\ and\ \citenamefont {Chen}}]{RN325}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
			{Daniels}}, \bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Wells}},\
		and\ \bibinfo {author} {\bibfnamefont {P.~C.}\ \bibnamefont {Chen}},\ }\href
	{https://doi.org/10.1063/5.0109084} {\bibfield  {journal} {\bibinfo
			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {157}},\
		\bibinfo {pages} {184201} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Chen}\ and\ \citenamefont
		{Daniels}(2024)}]{Chen2024}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~C.}\ \bibnamefont
			{Chen}}\ and\ \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
			{Daniels}},\ }\href {https://doi.org/10.1021/acs.jpclett.3c03254} {\bibfield
		{journal} {\bibinfo  {journal} {Journal of Physical Chemistry Letters}\
		}\textbf {\bibinfo {volume} {15}},\ \bibinfo {pages} {1234} (\bibinfo {year}
		{2024})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Dhar}\ \emph {et~al.}(1994)\citenamefont {Dhar},
		\citenamefont {Rogers},\ and\ \citenamefont {Nelson}}]{Dhar1994}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
			{Dhar}}, \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont {Rogers}},\
		and\ \bibinfo {author} {\bibfnamefont {K.~A.}\ \bibnamefont {Nelson}},\
	}\href {https://doi.org/10.1021/cr00025a006} {\bibfield  {journal} {\bibinfo
			{journal} {Chemical Reviews}\ }\textbf {\bibinfo {volume} {94}},\ \bibinfo
		{pages} {157} (\bibinfo {year} {1994})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Zhao}\ and\ \citenamefont {Wright}(1999)}]{RN345}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
			{Zhao}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
			{Wright}},\ }\href {https://doi.org/10.1103/PhysRevLett.83.1950} {\bibfield
		{journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
			{volume} {83}},\ \bibinfo {pages} {1950} (\bibinfo {year}
		{1999})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Cho}(2000)}]{Cho2000}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
			{Cho}},\ }\href {https://doi.org/10.1103/PhysRevA.61.023406} {\bibfield
		{journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
			{61}},\ \bibinfo {pages} {023406} (\bibinfo {year} {2000})}\BibitemShut
	{NoStop}%
	\bibitem [{\citenamefont {Boyle}\ \emph {et~al.}(2014)\citenamefont {Boyle},
		\citenamefont {Neff-Mallon}, \citenamefont {Handali},\ and\ \citenamefont
		{Wright}}]{RN491}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~S.}\ \bibnamefont
			{Boyle}}, \bibinfo {author} {\bibfnamefont {N.~A.}\ \bibnamefont
			{Neff-Mallon}}, \bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
			{Handali}},\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
			{Wright}},\ }\href {https://doi.org/10.1021/jp5018554} {\bibfield  {journal}
		{\bibinfo  {journal} {Journal of Physical Chemistry A}\ }\textbf {\bibinfo
			{volume} {118}},\ \bibinfo {pages} {3112} (\bibinfo {year}
		{2014})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Lee}\ and\ \citenamefont {Albrecht}(1985)}]{RN286}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
			{Lee}}\ and\ \bibinfo {author} {\bibfnamefont {A.~C.}\ \bibnamefont
			{Albrecht}},\ }\bibinfo {title} {A {U}nified {V}iew of {R}aman, {R}esonance
		{R}aman, and {F}luorescence {S}pectroscopy (and their {A}nalogues in
		{T}wo-{P}hoton {A}bsorption)},\ in\ \href@noop {} {\emph {\bibinfo
			{booktitle} {Advances in Infrared and Raman Spectroscopies}}},\ \bibinfo
	{editor} {edited by\ \bibinfo {editor} {\bibfnamefont {R.}~\bibnamefont
			{Clark}}\ and\ \bibinfo {editor} {\bibfnamefont {R.}~\bibnamefont {Hester}}}\
	(\bibinfo  {publisher} {Wiley},\ \bibinfo {address} {New York},\ \bibinfo
	{year} {1985})\ pp.\ \bibinfo {pages} {179--213}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Terhune}\ \emph {et~al.}(1965)\citenamefont
		{Terhune}, \citenamefont {Maker},\ and\ \citenamefont
		{Savage}}]{Terhune1965}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~W.}\ \bibnamefont
			{Terhune}}, \bibinfo {author} {\bibfnamefont {P.~D.}\ \bibnamefont {Maker}},\
		and\ \bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont {Savage}},\
	}\href {https://doi.org/10.1103/PhysRevLett.14.681} {\bibfield  {journal}
		{\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {14}},\
		\bibinfo {pages} {681} (\bibinfo {year} {1965})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Cyvin}\ \emph {et~al.}(1965)\citenamefont {Cyvin},
		\citenamefont {Rauch},\ and\ \citenamefont {Decius}}]{Cyvin1965}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
			{Cyvin}}, \bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont {Rauch}},\
		and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont {Decius}},\
	}\href {https://doi.org/10.1063/1.1696646} {\bibfield  {journal} {\bibinfo
			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {43}},\
		\bibinfo {pages} {4083} (\bibinfo {year} {1965})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Andrews}\ and\ \citenamefont
		{Thirunamachandran}(1978)}]{Andrews1978}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~L.}\ \bibnamefont
			{Andrews}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
			{Thirunamachandran}},\ }\href {https://doi.org/10.1063/1.436047} {\bibfield
		{journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
		{\bibinfo {volume} {68}},\ \bibinfo {pages} {2941} (\bibinfo {year}
		{1978})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Ziegler}(1990)}]{RN515}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~D.}\ \bibnamefont
			{Ziegler}},\ }\href {https://doi.org/10.1002/jrs.1250211203} {\bibfield
		{journal} {\bibinfo  {journal} {Journal of Raman Spectroscopy}\ }\textbf
		{\bibinfo {volume} {21}},\ \bibinfo {pages} {769} (\bibinfo {year}
		{1990})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Denisov}\ \emph {et~al.}(1986)\citenamefont
		{Denisov}, \citenamefont {Mavrin}, \citenamefont {Podobedov},\ and\
		\citenamefont {Sterin}}]{Denisov1986}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
			{Denisov}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Mavrin}},
		\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Podobedov}},\ and\
		\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Sterin}},\ }\href
	{https://doi.org/10.1016/0030-4018(86)90125-2} {\bibfield  {journal}
		{\bibinfo  {journal} {Optics Communications}\ }\textbf {\bibinfo {volume}
			{60}},\ \bibinfo {pages} {95} (\bibinfo {year} {1986})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Kozich}\ and\ \citenamefont
		{Werncke}(2007)}]{Kozich2007}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
			{Kozich}}\ and\ \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
			{Werncke}},\ }\href {https://doi.org/10.1002/jrs.1748} {\bibfield  {journal}
		{\bibinfo  {journal} {Journal of Raman Spectroscopy}\ }\textbf {\bibinfo
			{volume} {38}},\ \bibinfo {pages} {1180} (\bibinfo {year}
		{2007})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Kelley}(2010)}]{Kelley2010}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
			{Kelley}},\ }\href {https://doi.org/10.1146/annurev.physchem.012809.103347}
	{\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Physical
				Chemistry}\ }\textbf {\bibinfo {volume} {61}},\ \bibinfo {pages} {41}
		(\bibinfo {year} {2010})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Zilian}\ \emph {et~al.}(1994)\citenamefont {Zilian},
		\citenamefont {LaBuda}, \citenamefont {Hamilton}, \citenamefont {Chen},\ and\
		\citenamefont {Wright}}]{Zilian1994}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
			{Zilian}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont {LaBuda}},
		\bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont {Hamilton}}, \bibinfo
		{author} {\bibfnamefont {P.~C.}\ \bibnamefont {Chen}},\ and\ \bibinfo
		{author} {\bibfnamefont {J.~C.}\ \bibnamefont {Wright}},\ }\href
	{https://doi.org/10.1016/0022-2313(94)90242-9} {\bibfield  {journal}
		{\bibinfo  {journal} {Journal of Luminescence}\ }\textbf {\bibinfo {volume}
			{60-61}},\ \bibinfo {pages} {655} (\bibinfo {year} {1994})}\BibitemShut
	{NoStop}%
	\bibitem [{\citenamefont {Hamilton}\ \emph {et~al.}(1997)\citenamefont
		{Hamilton}, \citenamefont {LaBuda},\ and\ \citenamefont {Wright}}]{RN350}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont
			{Hamilton}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
			{LaBuda}},\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
			{Wright}},\ }\href {https://doi.org/10.1016/s0009-2614(97)00875-0} {\bibfield
		{journal} {\bibinfo  {journal} {Chemical Physics Letters}\ }\textbf
		{\bibinfo {volume} {277}},\ \bibinfo {pages} {175} (\bibinfo {year}
		{1997})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {LaBuda}\ and\ \citenamefont {Wright}(1997)}]{RN351}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
			{LaBuda}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
			{Wright}},\ }\href {https://doi.org/10.1103/PhysRevLett.79.2446} {\bibfield
		{journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
			{volume} {79}},\ \bibinfo {pages} {2446} (\bibinfo {year}
		{1997})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {LaBuda}\ and\ \citenamefont
		{Wright}(1998{\natexlab{a}})}]{RN352}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
			{LaBuda}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
			{Wright}},\ }\href {https://doi.org/10.1063/1.475809} {\bibfield  {journal}
		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
			{volume} {108}},\ \bibinfo {pages} {4112} (\bibinfo {year}
		{1998}{\natexlab{a}})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {LaBuda}\ and\ \citenamefont
		{Wright}(1998{\natexlab{b}})}]{RN353}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
			{LaBuda}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
			{Wright}},\ }\href {https://doi.org/10.1016/s0009-2614(98)00478-3} {\bibfield
		{journal} {\bibinfo  {journal} {Chemical Physics Letters}\ }\textbf
		{\bibinfo {volume} {290}},\ \bibinfo {pages} {29} (\bibinfo {year}
		{1998}{\natexlab{b}})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(1998)\citenamefont {Chen},
		\citenamefont {Hamilton}, \citenamefont {Zillan}, \citenamefont {LaBuda},\
		and\ \citenamefont {Wright}}]{Chen1998}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~C.}\ \bibnamefont
			{Chen}}, \bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont {Hamilton}},
		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zillan}}, \bibinfo
		{author} {\bibfnamefont {M.~J.}\ \bibnamefont {LaBuda}},\ and\ \bibinfo
		{author} {\bibfnamefont {J.~C.}\ \bibnamefont {Wright}},\ }\href
	{https://doi.org/10.1366/0003702981943563} {\bibfield  {journal} {\bibinfo
			{journal} {Applied Spectroscopy}\ }\textbf {\bibinfo {volume} {52}},\
		\bibinfo {pages} {380} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Murdoch}\ \emph {et~al.}(2000)\citenamefont
		{Murdoch}, \citenamefont {Thompson}, \citenamefont {Meyer},\ and\
		\citenamefont {Wright}}]{RN362}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~M.}\ \bibnamefont
			{Murdoch}}, \bibinfo {author} {\bibfnamefont {D.~E.}\ \bibnamefont
			{Thompson}}, \bibinfo {author} {\bibfnamefont {K.~A.}\ \bibnamefont
			{Meyer}},\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
			{Wright}},\ }\href {https://doi.org/10.1366/0003702001948411} {\bibfield
		{journal} {\bibinfo  {journal} {Applied Spectroscopy}\ }\textbf {\bibinfo
			{volume} {54}},\ \bibinfo {pages} {1495} (\bibinfo {year}
		{2000})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Thompson}\ and\ \citenamefont
		{Wright}(2000)}]{RN418}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~E.}\ \bibnamefont
			{Thompson}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
			{Wright}},\ }\href {https://doi.org/10.1021/jp002343p} {\bibfield  {journal}
		{\bibinfo  {journal} {Journal of Physical Chemistry A}\ }\textbf {\bibinfo
			{volume} {104}},\ \bibinfo {pages} {11282} (\bibinfo {year}
		{2000})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Hanninen}\ \emph {et~al.}(2018)\citenamefont
		{Hanninen}, \citenamefont {Prince}, \citenamefont {Ramos}, \citenamefont
		{Plikus},\ and\ \citenamefont {Potma}}]{Hanninen2018}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
			{Hanninen}}, \bibinfo {author} {\bibfnamefont {R.~C.}\ \bibnamefont
			{Prince}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Ramos}},
		\bibinfo {author} {\bibfnamefont {M.~V.}\ \bibnamefont {Plikus}},\ and\
		\bibinfo {author} {\bibfnamefont {E.~O.}\ \bibnamefont {Potma}},\ }\href
	{https://doi.org/10.1364/BOE.9.004807} {\bibfield  {journal} {\bibinfo
			{journal} {Biomed. Opt. Express}\ }\textbf {\bibinfo {volume} {9}},\ \bibinfo
		{pages} {4807} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2021)\citenamefont {Wang},
		\citenamefont {Wang}, \citenamefont {Shen}, \citenamefont {Han},
		\citenamefont {Li}, \citenamefont {He}, \citenamefont {Wang}, \citenamefont
		{Sokolov},\ and\ \citenamefont {Scully}}]{Wang2021}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
			{Wang}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Wang}}, \bibinfo
		{author} {\bibfnamefont {Y.}~\bibnamefont {Shen}}, \bibinfo {author}
		{\bibfnamefont {Z.}~\bibnamefont {Han}}, \bibinfo {author} {\bibfnamefont
			{F.}~\bibnamefont {Li}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
			{He}}, \bibinfo {author} {\bibfnamefont {D.-w.}\ \bibnamefont {Wang}},
		\bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont {Sokolov}},\ and\
		\bibinfo {author} {\bibfnamefont {M.~O.}\ \bibnamefont {Scully}},\ }\href
	{https://doi.org/10.1021/acsphotonics.0c01940} {\bibfield  {journal}
		{\bibinfo  {journal} {ACS Photonics}\ }\textbf {\bibinfo {volume} {8}},\
		\bibinfo {pages} {1137} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Seliya}\ \emph {et~al.}(2024)\citenamefont {Seliya},
		\citenamefont {Bonn},\ and\ \citenamefont {Grechko}}]{Bonn2024}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
			{Seliya}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bonn}},\ and\
		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Grechko}},\ }\href
	{https://doi.org/10.1063/5.0179041} {\bibfield  {journal} {\bibinfo
			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {160}},\
		\bibinfo {pages} {034201} (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {McDonnell}\ \emph {et~al.}(2024)\citenamefont
		{McDonnell}, \citenamefont {Oram}, \citenamefont {Boyer}, \citenamefont
		{Kohler}, \citenamefont {Meyer}, \citenamefont {Sibert~III},\ and\
		\citenamefont {Wright}}]{McDonnell2024}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~P.}\ \bibnamefont
			{McDonnell}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Oram}},
		\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Boyer}}, \bibinfo
		{author} {\bibfnamefont {D.~D.}\ \bibnamefont {Kohler}}, \bibinfo {author}
		{\bibfnamefont {K.~A.}\ \bibnamefont {Meyer}}, \bibinfo {author}
		{\bibfnamefont {E.~L.}\ \bibnamefont {Sibert~III}},\ and\ \bibinfo {author}
		{\bibfnamefont {J.~C.}\ \bibnamefont {Wright}},\ }\href
	{https://doi.org/10.1021/acs.jpclett.4c00297} {\bibfield  {journal} {\bibinfo
			{journal} {Journal of Physical Chemistry Letters}\ }\textbf {\bibinfo
			{volume} {15}},\ \bibinfo {pages} {3975} (\bibinfo {year}
		{2024})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Armstrong}\ \emph {et~al.}(1962)\citenamefont
		{Armstrong}, \citenamefont {Bloembergen}, \citenamefont {Ducuing},\ and\
		\citenamefont {Pershan}}]{RN480}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
			{Armstrong}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
			{Bloembergen}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
			{Ducuing}},\ and\ \bibinfo {author} {\bibfnamefont {P.~S.}\ \bibnamefont
			{Pershan}},\ }\href {https://doi.org/10.1103/PhysRev.127.1918} {\bibfield
		{journal} {\bibinfo  {journal} {Physical Review}\ }\textbf {\bibinfo {volume}
			{127}},\ \bibinfo {pages} {1918} (\bibinfo {year} {1962})}\BibitemShut
	{NoStop}%
	\bibitem [{\citenamefont {Ivanecky~III}\ and\ \citenamefont
		{Wright}(1993)}]{RN243}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
